---
title: "Word Prediction Presentation"
author: "Andrew Dieterich"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project Overview

In this presentation we are looking at how to take twitter, blog post, and news strings of text
And make them into one, two, three, and four n-grams using a text mining package (quanteda)
With the goal of doing text next-word prediction similarly to Swift Key

## Background Information

 - n-gram background info: https://en.wikipedia.org/wiki/N-gram
 
 - R Studio Shiny App page: https://www.shinyapps.io
 
 - Text Mining in R: https://www.coursera.org/learn/data-science-project/supplement/FrBtO/project-overview

 - Data Source: https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip


## Code Examples

```{r, eval=FALSE}
set.seed(1234567)
data.sample <- sample(twitter, length(twitter) * 0.10)
saveRDS(data.sample, 'sample_text_twitter.rds')
twitter_sample <- readRDS("sample_text_twitter.rds")

Sample_twitter <- corpus(twitter_sample)
token_twitter <- tokens(Sample_twitter, remove_separators = TRUE, remove_punct = TRUE)
token_twitter <- tokens_remove(token_twitter, pattern = stopwords('en'))
token_twitter <- tokens_wordstem(token_twitter)
token_twitter <- tokens_tolower(token_twitter)

ngram_twitter <- tokens_ngrams(token_twitter, n = 1)
top_ngrams_twitter <- topfeatures(dfm(ngram_twitter), 20)

barplot(height = top_ngrams_twitter, names.arg = names(top_ngrams_twitter),
        las = 2, main = "One n-gram frequency of Twitter sample")
```

## How to Use the Shiny App
To use the shiny app, you only need to enter text into the text box

Then select how many words (on the slider) to be predicted

Then click the button, and observe the output words that are predicted

By the model, based on the compiled n-gram .Rdata file

## File links

 - The Github folder is here

 - And the Shiny App can be found here

Thank you!

